---
title: "Indonesia Jarvis Report"
author: "[Gourab Chanda](https://eur.delve.office.com/?u=3590af90-5c56-4bab-b266-774c53b44384&v=work)"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Introduction

This report provide the details about the **Indonesia Jarvis Bango** data blending process build using *R* software and it's packages.The process has been developed using `r R.version.string`. The data blending model is build for the brand named **Bango**. The brand is under the category **Savoury** and sector **Seasoning**. 

There are total 9 Internal data sources which are as mentioned below in chronological sequence as mentioned below -

* **
* **Dispatch Rate**.
* **Primary Sales**.
* **Secondary Sales**.
* **Secondary Stock**.
* **Trade Term Structure**.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
